A thesis draft

### 2018-11-26 res/sections/15-ArchitecturalImplementation.tex
Fix typos

The impossibility to develop a custom VIM driver and VNFM manager lead us to
search for an alternative solution. Then, we started work directly on the VIM.
The base approach was to create an API Server which in future an Openbaton
plugin could contact and simply deploy TOSCA definitions, interacting with a set
of RESTful API.

>>>>

The impossibility to develop a custom VIM driver and VNFM manager lead us to
search for an alternative solution. Then, we started to work directly on the
VIM. The base approach was to create an API Server which in future an Openbaton
plugin could contact and simply deploy TOSCA definitions, interacting with a set
of RESTful APIs.
